Draft Exploratory Analysis

### 2024-11-06 Data_Cleaning_20241031.Rmd
Update to Draft Exploratory Analysis
Included spatial map as evidence for our decision to restrict analysis to Great Plains

ggplot(graph1_data, aes(x = year, y = total_population)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Bison Population by State - Some Major Locations", x = "Year", y = "Bison Population") +
  facet_wrap(~state_code)

ggplot(graph2_data, aes(x = year, y = total_population)) + 
  xlab("Year") +
  ylab("Population") +
  labs(title = "Bison Population Over Time") +
  geom_point(aes(color = state_code), size = 3) +
  geom_smooth()

ggplot(graph2_data, aes(x = year, y = `Gross Cost - Hunting Licenses`)) + 
  xlab("Year") +
  ylab("Population") +
  labs(title = "Gross Cost of Hunting Licenses Over Time") +
  geom_point(aes(color = state_code), size = 3) +
  geom_smooth()

#Looking for relationship between number of hunting licenses and population
ggplot(merged_bison_data, aes(x = `Paid Hunting License Holders`, y = total_population)) +
  geom_point() + geom_smooth()
```

>>>>

graph3_data = merged_bison_data |>
  filter(state_code == "TEXAS")

#Some major state populations... all trends look different
ggplot(graph1_data, aes(x = year, y = total_population)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Bison Population by State - Some Major Locations", x = "Year", y = "Bison Population") +
  facet_wrap(~state_code)

#Overall trends across the great plains... see downward trend overall
ggplot(graph2_data, aes(x = year, y = total_population)) + 
  xlab("Year") +
  ylab("Population") +
  labs(title = "Bison Population Over Time") +
  geom_point(aes(color = state_code), size = 3) +
  geom_smooth()

#Number of Hunting licenses Over Time
ggplot(graph2_data, aes(x = year, y = `Paid Hunting License Holders`)) + 
  xlab("Year") +
  ylab("Population") +
  labs(title = "Number of Licenses Over Time") +
  geom_point(aes(color = state_code), size = 3) +
  geom_smooth()

#Looking for relationship between number of hunting licenses and population
ggplot(merged_bison_data, aes(x = `Paid Hunting License Holders`, y = total_population)) +
  geom_point() + 
  geom_smooth() +
  xlab("Number of Lisense Holders") +
  ylab("Population") +
  labs(title = "Number of Licenses vs Population")
```

### 2024-11-06 Draft Exploratory Analysis.Rmd
Update to Draft Exploratory Analysis
Included spatial map as evidence for our decision to restrict analysis to Great Plains

  After realizing that there is some variety in the details of population growth or decline across states, we sought to confirm our suspician that the overall population trend is negative. What we see in the following graph is a confirmation of that suspicion, where population sees a strong downward trend across the Great Plains:
![Great Plains Population Over Time - Overall Trend](C:/Users/kdfro/Documents/MSU/GitHub/ECNS-560-Term-Project/Visuals/Population Over Time.png)

>>>>

  After realizing that there is some variety in the details of population growth or decline across states, we sought to confirm our suspicion that the overall population trend is negative. What we see in the following graph is a confirmation of that suspicion, where population sees a strong downward trend across the Great Plains:
![Great Plains Population Over Time - Overall Trend](C:/Users/kdfro/Documents/MSU/GitHub/ECNS-560-Term-Project/Visuals/Population Over Time.png)

  As a side note, our decision to restrict our focus to the Great Plains was based off of our spatial data which indicates to us that the majority of Bison herds are concentrated in these states, as shows in the following image:
![Bison Herds in the U.S.](C:/Users/kdfro/Documents/MSU/GitHub/ECNS-560-Term-Project/Visuals/Range Map.png)
